---
title: "FARS vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FARS vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(practicepackage)
```

The package contains functions for reading, summarizing and plotting FARS data.

## Read data

Data is expected to be saved in compressed csv files named like accident_YYYY.csv.bz2 where YYYY indicates the year.
Data from multiple files can be read with a single function call.

```{r read, eval = FALSE}
y <- c(2017, 2018, 2019)
fars_data <- fars_read_years(y)
```

## Summarize data

Show number of accidents per month.

```{r summarize, eval = FALSE}
y <- c(2017, 2018, 2019)
fars_summary <- fars_summarize_years(y)
```

## Plot accidents on map

A map showing accidents in any US state can be plotted using `fars_map_state` function.

For example to plot accidents of California (FIPS code = 6) for year 2013:

```{r plot, eval = FALSE}
fars_map_state(6, 2013)
```

